---
title: "si_w4"
author: "Arturo Garcia"
date: "7/6/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
lambda <- 0.2

simulations <- matrix(rexp(40000,lambda), ncol = 40)

averages <- rowMeans(simulations)

sample_mean <- mean(averages)
sample_sd <- sd(averages)

hist(rexp(1000,lambda))

hist(averages)
```

#Part 2 

```{r}
data(ToothGrowth)
?ToothGrowth
```
***
>
*ToothGrowth {datasets}*     
**The Effect of Vitamin C on Tooth Growth in Guinea Pigs**
>
Description

>The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery methods, (orange juice or ascorbic acid (a form of vitamin C and coded as VC).

>Usage

>ToothGrowth
>Format

>A data frame with 60 observations on 3 variables.

>[,1]	 len	 numeric	 Tooth length   
>[,2]	 supp	 factor	 Supplement type (VC or OJ).   
>[,3]	 dose	 numeric	 Dose in milligrams/day    

>Source
>C. I. Bliss (1952) The Statistics of Bioassay. Academic Press.

***



```{r}
with(ToothGrowth, t.test(len ~ supp))

head(ToothGrowth)
str(ToothGrowth)
```

